Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
fix adobe error

@@

@@

@@

@@

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline Distance from wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\ \hline
		\hline 0.61 				& 1 				& 1 				& 2 			 	\\
		\hline 0.31					& 3	 				& 1					& 2 			 	\\
		\hline 0.15					& 1				 	& 1					& 2 			 	\\
		\hline 0.08					& 0 				& 1 				& 2 	 			\\
		\hline 0.00					& 1 				& 1 				& 3 	 			\\
		\hline
	\end{tabular}
	\caption[Matrix of instrumented gypsum wallboard experiments]{Matrix of instrumented gypsum wallboard experiments}
	\label{tab:IWGB_experiments}
\end{table}

\begin{figure}[p]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Plume_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Plume_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Plume_Avg}\\
	\caption[Plume temperatures for the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner.    Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
	\label{IWGB_NG_TC_Plume_set}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Surface_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Surface_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Surface_Center_Avg}\\
	\caption[Front surface wall temperatures for the natural gas fueled burner]{Front surface wall temperatures for the natural gas fueled burner. Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
	\label{IWGB_NG_TC_Wall_set}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Back_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Back_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Back_Center_Avg}\\
	\caption[Backside wall temperatures for the natural gas fueled burner]{Backside wall temperatures along the centerline of the natural gas fueled burner. Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
	\label{IWGB_NG_TC_Backside_set}
\end{figure}

 \begin{figure}[p]
 	\centering
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_HF_Center_Avg}\\
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_HF_Center_Avg}\\
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_HF_Center_Avg}\\
 \caption[Wall heat flux along the centerline of the natural gas fueled burner]{Wall heat flux along the vertical centerline of the natural gas fueled burner. Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
 	\label{IWGB_NG_HF_CenterSet}
 \end{figure}

 \begin{figure}[p]
 	\centering
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_HF_Offset_Avg}\\
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_HF_Offset_Avg}\\
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_HF_Offset_Avg}\\
 	\caption[Wall heat flux along the edge of the natural gas fueled burner]{Wall heat flux along the edge of the natural gas fueled burner. Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
 	\label{IWGB_NG_HF_EdgeSet}
 \end{figure}

\begin{figure}
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Offset_Avg}\\
	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires. }
	\label{IWGB_NG_HF_CandEAvg}
\end{figure}

@@

A summary of the peak average temperatures and heat fluxes at the wall is provided in Table~\ref{tab:IWGB_Summary}. While the values in this summary table differ from the values in Table~\ref{tab:TW_Summary} a closer look reveals that most of the values are not ``significantly '' different.  In other words the range of expanded uncertainty values overlap.  For example at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$pm$73~$^\circ$C (15~\%). So the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.  While all of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are ``that '' different.

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline {Burner} & \multicolumn{2}{c}{Natural Gas} & \multicolumn{2}{c}{Gasoline} & \multicolumn{2}{c|}{PU Foam} \\
		\hline  Position & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) 	\\
		\hline \hline 0.61~m & 132 & 4 & 109 & 6 & 76 & 4 \\
		\hline 0.31~m & 160 & 11 & 185 & 18 & 151 & 12	\\
		\hline 0.15~m & 250 & 23 & 377 & 57 & 244 & 25	\\
		\hline 0.00~m & 539 & 55 & 590 & 61 & 415 & 59 	\\
		\hline
	\end{tabular}
	\caption[Summary of instrumented gypsum wallboard experiments]{Summary of averaged peak temperatures and heat fluxes from the instrumented gypsum wallboard experiments.  The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for the heat flux.} 
	\label{tab:IWGB_Summary}
\end{table}

>>>>

\begin{table}[ht!]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline Distance from wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\ \hline
		\hline 0.61 				& 1 				& 1 				& 2 			 	\\
		\hline 0.31					& 3	 				& 1					& 2 			 	\\
		\hline 0.15					& 1				 	& 1					& 2 			 	\\
		\hline 0.08					& 0 				& 1 				& 2 	 			\\
		\hline 0.00					& 1 				& 1 				& 3 	 			\\
		\hline
	\end{tabular}
	\caption[Matrix of instrumented gypsum wallboard experiments]{Matrix of instrumented gypsum wallboard experiments}
	\label{tab:IWGB_experiments}
\end{table}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Plume_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Plume_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Plume_Avg}\\
	\caption[Plume temperatures for the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner.    Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
	\label{IWGB_NG_TC_Plume_set}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Surface_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Surface_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Surface_Center_Avg}\\
	\caption[Front surface wall temperatures for the natural gas fueled burner]{Front surface wall temperatures for the natural gas fueled burner. Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
	\label{IWGB_NG_TC_Wall_set}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Back_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Back_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Back_Center_Avg}\\
	\caption[Backside wall temperatures for the natural gas fueled burner]{Backside wall temperatures along the centerline of the natural gas fueled burner. Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
	\label{IWGB_NG_TC_Backside_set}
\end{figure}

\clearpage

@@

 \begin{figure}[ht!]
 	\centering
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_HF_Center_Avg}\\
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_HF_Center_Avg}\\
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_HF_Center_Avg}\\
 \caption[Wall heat flux along the centerline of the natural gas fueled burner]{Wall heat flux along the vertical centerline of the natural gas fueled burner. Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
 	\label{IWGB_NG_HF_CenterSet}
 \end{figure}

  \begin{figure}[ht!]
 	\centering
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_HF_Offset_Avg}\\
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_HF_Center_Avg}\\
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_HF_Offset_Avg}\\
 \caption[Wall heat flux along the endge of the natural gas fueled burner]{Wall heat flux along the vertical edge of the natural gas fueled burner. Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.  Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
 	\label{IWGB_NG_HF_EdgeSet}
 \end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Center_Avg}\\
	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Offset_Avg}\\
	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires.}
	\label{IWGB_NG_HF_CandEAvg}
\end{figure}

\clearpage

@@

A summary of the peak average temperatures and heat fluxes at the wall is provided in Table~\ref{tab:IWGB_Summary}. While the values in this summary table differ from the values in Table~\ref{tab:TW_Summary} a closer look reveals that most of the values are not ``significantly '' different.  In other words the range of expanded uncertainty values overlap.  For example at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$\pm$73~$^\circ$C (15~\%). So the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.  While all of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are ``that '' different.

\begin{table}
	\centering
	\scriptsize
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline {Burner} & \multicolumn{2}{c}{Natural Gas} & \multicolumn{2}{c}{Gasoline} & \multicolumn{2}{c|}{PU Foam} \\
		\hline  Position & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) 	\\
		\hline \hline 0.61~m & 132 & 4 & 109 & 6 & 76 & 4 \\
		\hline 0.31~m & 160 & 11 & 185 & 18 & 151 & 12	\\
		\hline 0.15~m & 250 & 23 & 377 & 57 & 244 & 25	\\
		\hline 0.00~m & 539 & 55 & 590 & 61 & 415 & 59 	\\
		\hline
	\end{tabular}
	\caption[Summary of instrumented gypsum wallboard experiments]{Summary of averaged peak temperatures and heat fluxes from the instrumented gypsum wallboard experiments.  The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for the heat flux.} 
	\label{tab:IWGB_Summary}
\end{table}
